Multiple Comparisons in Toolmark Evidence

### 2023-11-20 LPR/index.qmd
Add extra sections of the intro

>>>>

### Examination Process

### Comparison counts

When assessing the total number of comparisons, we will consider two extremes: first, a set of completely independent comparisons made by dividing the blade cut up into a series of non-overlapping segments the same size as the wire. XXX add picture XXX The second extreme is a series of comparisons made by sliding the wire along the blade cut in increments equal to the resolution of the scan or optical viewer (depending on whether this comparison is done automatically or visually). Of course, the reality is that an algorithm or examiner will likely make a number of comparisons between these two extremes, however, rather than consider all possible comparison numbers within this span, it is more efficient to explore what happens at each endpoint first.
